---
title: "bincor"
author: "Anna Urbala"
date: "11 maja 2020"
output: pdf_document
---

# BINCOR: An R package for Estimatingthe Correlation between Two UnevenlySpaced Time Series
## *by Josue M. Polanco-Martinez, Martin A. Medina-Elizalde, Maria Fernanda Sanchez Goni, ManfredMudelsee*
[Link](https://journal.r-project.org/archive/2019/RJ-2019-035/RJ-2019-035.pdf)

```{r, cache=TRUE, error=TRUE}
# Load the package
library(BINCOR)
# Load the time series under analysis: Example 1 and Figure 1 (ENSO vs. NHSST)
data(ENSO)
data(NHSST)
# Compute the binned time series though our bin_cor function
bincor.tmp <- bin_cor(ENSO.dat, NHSST.dat, FLAGTAU=3, "output_ENSO_NHSST.tmp")

binnedts   <- bincor.tmp$Binned_time_series
# Applying our plot_ts function
# "Screen"
plot_ts(ENSO.dat, NHSST.dat, binnedts[,1:2], binnedts[,c(1,3)], "ENSO-Nino3","SST NH Mean", colts1=1, colts2=2, colbints1=3, colbints2=4, device="screen")
```

Wykresy zbliżone. Niestety znowu proporcje zależą od ustawień.

```{r, cache=TRUE, error=TRUE}
# Load packages
library(BINCOR)
library(pracma)
# Load the time series under analysis: Example 1 and Figure 2 (ENSO vs. NHSST)
data(ENSO)
data(NHSST)
# Compute the binned time series though our bin_cor function
bincor.tmp <- bin_cor(ENSO.dat, NHSST.dat, FLAGTAU=3, "output_ENSO_NHSST.tmp")
binnedts   <- bincor.tmp$Binned_time_series
# Compute the scatterplot by means of our function cor_ts
# PDF format (scatterplot) and Pearson
cor_ts(binnedts[,1:2], binnedts[,c(1,3)], "ENSO-Nino3", "SST NH Mean",KoCM="pearson", rmltrd="y", device="pdf", Hpdf=6, Wpdf=9, resfig=300,ofilename="scatterplot_ENSO_SST")
```

ok

```{r, cache=TRUE, error=TRUE}
# Load the package
library(BINCOR)
library(pracma)
# Load the time series under analysis: Example 2 and Figure 6
data(MD04_2845_siteID31)
data(MD95_2039_siteID32)
# Compute the binned time series though our bin_cor function
bincor.tmp <- bin_cor(ID31.dat, ID32.dat, FLAGTAU=3, "salida_ACER_ABRUPT.tmp")
binnedts   <- bincor.tmp$Binned_time_series
# To avoid NA values
bin_ts1 <- na.omit(bincor.tmp$Binned_time_series[,1:2])
bin_ts2 <- na.omit(bincor.tmp$Binned_time_series[,c(1,3)])
# Applying our plot_ts function
# PDF format
plot_ts(ID31.dat, ID32.dat, bin_ts1, bin_ts2, "MD04-2845 (Temp. forest)","MD95-2039 (Temp. forest )", colts1=1, colts2=2, colbints1=3, colbints2=4,device="pdf", Hpdf=6, Wpdf=9, resfig=300, ofilename="ts_ACER_ABRUPT")
```
delikatna różnica w proporcjach, inne odległości punktów od osi

```{r, cache=TRUE, error=TRUE}
# Load packages
library(BINCOR)
library(pracma)
# Load the time series under analysis: Example 2 and Figure 7 (ID31 vs. ID32)data(MD04_2845_siteID31)
data(MD95_2039_siteID32)
# Compute the binned time series though our bin_cor function
bincor.tmp <- bin_cor(ID31.dat, ID32.dat, FLAGTAU=3, "salida_ACER_ABRUPT.tmp")
binnedts   <- bincor.tmp$Binned_time_series
# To avoid NA values
bin_ts1 <- na.omit(bincor.tmp$Binned_time_series[,1:2])
bin_ts2 <- na.omit(bincor.tmp$Binned_time_series[,c(1,3)])
# Applying our ccf_ts function
# PDF format
ccf_acf <- ccf_ts(bin_ts1, bin_ts2, RedL=TRUE, rmltrd="y", device="pdf", Hpdf=6,Wpdf=9, resfig=300, ofilename="ccf_ID31_ID32_res")
```

ok

## Problemy 
- czasem inne proporcje


# Podsumowanie
| Kategoria | Ocena |
|-----------|-------|
| Dostęp do zewnętrznych zasobów |`r icon::fa("minus")` `r icon::fa("minus")` `r icon::fa("minus")` `r icon::fa("minus")` `r icon::fa("minus")`|
| Kompatybilność z nowszymi wersjami |`r icon::fa("plus")` `r icon::fa("plus")` `r icon::fa("plus")` `r icon::fa("plus")` `r icon::fa("plus")`|
| Kwestie graficzne/estetyczne |`r icon::fa("plus")` `r icon::fa("plus")` `r icon::fa("plus")` `r icon::fa("plus")` `r icon::fa("times")`|
| Brak problemów przy dodatkowej konfiguracji | `r icon::fa("minus")` `r icon::fa("minus")` `r icon::fa("minus")` `r icon::fa("minus")` `r icon::fa("minus")` |
| Odporność na wpływ losowości |`r icon::fa("minus")` `r icon::fa("minus")` `r icon::fa("minus")` `r icon::fa("minus")` `r icon::fa("minus")`|
| Dostępność kodów źródłowych |`r icon::fa("plus")` `r icon::fa("plus")` `r icon::fa("plus")` `r icon::fa("plus")` `r icon::fa("plus")`|


### Session info
```{r, echo=FALSE, cache=TRUE}
sessionInfo()
```