---
title: "Geospatial Point Density"
author: "Anna Urbala"
date: "1 maja 2020"
output: pdf_document
---
# Geospatial Point Density
# *by Paul F. Evangelista and David Beskow*
[Link](https://journal.r-project.org/archive/2018/RJ-2018-061/RJ-2018-061.pdf)

```{r error=TRUE, cache=TRUE}
library(ggmap)
library(KernSmooth)
library(pointdensityP)
# BKDE2D script (figure 1)
# edit line below to read data from file location
SD<-read.table("extra/GeospatialPointDensity/incidents-5y.csv", sep = ",", header = TRUE)
x<-cbind(SD$lon,SD$lat)
est<-bkde2D(x,bandwidth=c(.01,.01),gridsize=c(750,800),range.x=list(c(-117.45,-116.66),c(32.52,33.26)))
BKD_df <- data.frame(lat=rep(est$x2, each = 750),lon=rep(est$x1, 800),count=c(est$fhat))
map_base <- qmap(location="32.9,-117.1", zoom = 10, darken=0.3)
png("SD_bkde2D_test.png", width = 1000, height = 1000, units = "px")
map_base+stat_contour(bins=150,geom="polygon",aes(x=lon, y=lat, z=count, fill = ..level..), data = BKD_df, alpha = 0.15) + scale_fill_continuous(name = "kernel density\nestimate\n", low = "green", high = "red") + labs(color = "density count\n1km radius\n") + theme(legend.position = c(0.1, 0.2), legend.background = element_rect(fill = NA), legend.key.size = unit(1, "cm"),  legend.text = element_text(size = 15), legend.title = element_text(size = 20))
dev.off()
```

```{r error=TRUE, cache=TRUE, results="hide"}
# point density script (figure 2)
SD_density <- pointdensity(df = SD, lat_col = "lat", lon_col = "lon", date_col = "date", grid_size = 0.1, radius = 1)
SD_density$count[SD_density$count>10000] <- 10000 ## creates discriminating scale
png("SD_pointdensity_test.png", width = 1000, height = 1000, units = "px")
map_base + geom_point(aes(x = lon, y = lat, colour = count), shape = 16, size = 0.5, data = SD_density) + scale_colour_gradient(low = "green", high = "red") + labs(color = "density count\n1km radius\n") + theme(legend.position = c(0.1, 0.2), legend.background = element_rect(fill = NA), legend.key.size = unit(1, "cm"),  legend.text = element_text(size = 15), legend.title = element_text(size = 20))
dev.off()
```

Przez brak dostępu do API nie można wykonać obrazków przedstawionych w artykule:

```{r, cache=TRUE, echo=FALSE}
library(png)
library(grid)
img <- readPNG("extra/GeospatialPointDensity/01.png")
grid.raster(img)
img <- readPNG("extra/GeospatialPointDensity/02.png")
grid.raster(img)
```

```{r error=TRUE, cache=TRUE}
# temporal tendency script (figure 3)
SD_temp_tend <- SD_density[SD_density$dateavg > 0]
#trim upper and lower tails for discriminating visualization
SD_temp_tend$dateavg[SD_temp_tend$dateavg<14711] <- 14711
SD_temp_tend$dateavg[SD_temp_tend$dateavg>14794] <- 14794
png("SD_temp_tend_test.png", width = 1000, height = 1000, units = "px")
map_base + geom_point(aes(x = lon, y = lat, colour = dateavg), shape = 16, size = 0.5, data = SD_temp_tend) + scale_colour_gradient(low = "green", high = "red")
dev.off()
```
Znowu mamy problem z uzyskaniem grafiki przez brak obiektu pobranego z API Google'a.

```{r, cache=TRUE}
#histogram plots in figure 3 and simple linear regression model to measure trends
#San Diego Crime Set
x <- as.Date(SD$date)
hist(x,"weeks",format = "%d %b %y", freq = TRUE, xlab = "week", ylab = "count of reported crime", main = "weekly count of crime")
res <- hist(x,"weeks",format = "%d %b %y", freq = TRUE)
SanDiegoTotal <- res$breaks[1:(length(res$breaks)-1)]
model <- lm(res$counts ~ SanDiegoTotal)
summary(model)
```

```{r, cache=TRUE}
#Mid-city
mid_city <- subset(SD, lat > 32.69 & lon > -117.14 & lat < 32.79 & lon < -117.08)
x <- as.Date(mid_city$date)
hist(x,"weeks",format = "%d %b %y", freq = TRUE) 
res <- hist(x,"weeks",format = "%d %b %y", freq = TRUE)
xres <- res$breaks[1:(length(res$breaks)-1)]
model <- lm(res$counts ~ xres)
summary(model)
```

```{r, cache=TRUE}
#Encinitas
encinitas <- subset(SD, lat > 33 & lon > -117.32 & lat < 33.09 & lon < -117.27)
x <- as.Date(encinitas$date)
hist(x,"weeks",format = "%d %b %y", freq = TRUE)
res <- hist(x,"weeks",format = "%d %b %y", freq = TRUE)
xres <- res$breaks[1:(length(res$breaks)-1)]
model <- lm(res$counts ~ xres)
summary(model)
```

Powyższe histogramy są takie jak w artykule:

```{r, cache=TRUE, echo=FALSE}
library(png)
library(grid)

img <- readPNG("extra/GeospatialPointDensity/05.png")
grid.raster(img)
```

Również statystyki są takie same:

```{r, cache=TRUE, echo=FALSE}
library(png)
library(grid)

img <- readPNG("extra/GeospatialPointDensity/06.png")
grid.raster(img)
```

```{r, cache=TRUE}
## Remaining code in the file supports the time comparison shown in table 1
#pointdensity_original() below is necessary to run the timed comparisons between the hash-based and matrix-based algorithms 
pointdensity_original <- function(df, lat_col, lon_col, date_col = NULL, grid_size, radius){
  
  grid_size <- round(grid_size/111.2, digits = 3)
  rad_km <- radius 			## initial radius measurement in km
  rad_dg <- rad_km/111.2  		## radius as a latitudinal distance
  rad_steps <- round(rad_dg/grid_size)  ## number of steps within grid 
  rad_km <- rad_steps * grid_size * 111.2	## radius rounded to nearest grid step
  cat("\nThe radius was adjusted to ",rad_km,"km in order to accomodate the grid size\n\n") 
  cat("algorithm grid step radius is ",rad_steps,"\n\n")
  radius <- rad_steps  			## assign to original variable
  h<-new.env(hash=TRUE)  		## hash that will store the density count
  avg_date<-new.env(hash=TRUE) 		## hash that will store the average date
  bh <- new.env(hash=TRUE)		## hash that will store the binned density count for a point
  b_date<-new.env(hash=TRUE)		## hash that will store the binned date cont for a point
  
  #round all latitude data to nearest grid	
  lat_data <- df[,lat_col]
  lat<-lat_data*(1/grid_size)
  lat<-round(lat,0)
  lat<-lat*(grid_size)
  #round all longitude data to nearest grid
  lon_data <- df[,lon_col]
  lon<-lon_data*(1/grid_size)
  lon<-round(lon,0)
  lon<-lon*(grid_size)
  if(is.null(date_col)){
    date <- rep(0,length(lon))
  }
  if(!is.null(date_col)){
    date <- as.Date(df[,date_col])
    date <- as.numeric(date)
  }
  key.vec<-paste(lat,lon,sep="-")
  
  data_length <- length(lat)
  ulat <- c()
  ulon <- c()
  cat("binning data...\n\n")
  pb <- txtProgressBar(title="point density calculation progress", label="0% done", min=0, max=100, initial=0, style = 3)
  for(i in 1:data_length){
    key<-paste(lat[i], lon[i], sep="-")
    if(is.null(h[[key]])){
      bh[[key]]=1
      h[[key]]=1
      b_date[[key]]=date[i]
      avg_date[[key]] = b_date[[key]]
      ulat <- c(ulat,lat[i])
      ulon <- c(ulon,lon[i])
    }
    else{
      bh[[key]]<-bh[[key]]+1
      h[[key]]<-bh[[key]]
      b_date[[key]] = b_date[[key]] + date[i]
      avg_date[[key]] = b_date[[key]]
    }
    #cat("\n",i,lat[i],lon[i],h[[key]],avg_date[[key]],"\n")
    setTxtProgressBar(pb, i/(data_length)*100, label=info)
  }
  cat("\n", "Data length is ", data_length, "; reduced to ", length(ulat), "bins. Density calculation starting.\n\n")
  lat <- ulat
  lon <- ulon
  
  pb <- txtProgressBar(title="point density calculation progress", label="0% done", min=0, max=100, initial=0, style = 3)
  counter<-0
  data_length <- length(lat)
  pb2 <- txtProgressBar(title="point density calculation progress", label="0% done", min=0, max=100, initial=0, style = 3)
  
  for(i in 1:data_length){
    counter <- counter + 1
    if(counter > 99){
      flush.console()
      counter <- 0
    }
    ukey<-paste(lat[i], lon[i], sep="-")    
    lat.vec<-seq(lat[i]-radius*grid_size,lat[i]+radius*grid_size,grid_size)
    for(lat.temp in lat.vec){
      t<-sqrt(round(((radius*grid_size)^2-(lat.temp-lat[i])^2),8))
      t<-t/cos(lat.temp*2*pi/360)
      t<-t/grid_size
      t<-round(t,0)
      t<-t*grid_size
      lon.vec<-seq(lon[i]-t,lon[i]+t,grid_size)
      for(lon.temp in lon.vec){
        key<-paste(lat.temp, lon.temp, sep="-")
	if(is.null(h[[key]])){
          h[[key]]=bh[[ukey]]
          avg_date[[key]]=b_date[[ukey]]
        }
        else{
	  if(key != ukey){
	    h[[key]]<-h[[key]]+bh[[ukey]]
            avg_date[[key]] = avg_date[[key]] + b_date[[ukey]]
	  }
	}
	#cat(lat.temp,lon.temp,h[[key]],avg_date[[key]],"\n")
      }
    }
   #cat("\n here again ",ukey, lat[i],lon[i],h[[ukey]],"avg_date", avg_date[[ukey]],"\n")
   info <- sprintf("%d%% done", round((i/data_length)*100)) 
   #setWinProgressBar(pb, i/(data_length)*100, label=info)
   setTxtProgressBar(pb2, i/(data_length)*100, label=info)
  }
  close(pb)
  count_val <- rep(0,length(key.vec))
  avg_date_val <- rep(0,length(key.vec))
  
 for(i in 1:length(key.vec)){
    count_val[i] <- h[[key.vec[i]]]	
    avg_date_val[i] <- avg_date[[key.vec[i]]]/count_val[i]
    count_val[i] <- count_val[i]/(pi*rad_km^2)
  }
  final<-data.frame(lat=lat_data,lon=lon_data,count=count_val,dateavg = avg_date_val)
  final<-final[order(final$count),]
  return(final)
  cat("done...\n\n")	
}
```

```{r, cache=TRUE, results="hide"}
matrix_time <- rep(0,6)
hash_time <- rep(0,6)
data_size <- rep(0,6)
for(i in 1:6){
  number_rows = 10^i
  SD_sample <- SD[sample(nrow(SD),number_rows,replace = TRUE),]
  data_size[i] = number_rows
  
  ptm <- proc.time()
  SD_density_original <- pointdensity_original(df = SD_sample, lat_col = "lat", lon_col = "lon", date_col = "date", grid_size = 0.1, radius = 1)
  proc_time_original <- proc.time() - ptm
  hash_time[i] = proc_time_original[[3]] 
  
  ptm <- proc.time()
  SD_density_n <- pointdensity(df = SD_sample, lat_col = "lat", lon_col = "lon", date_col = "date", grid_size = 0.1, radius = 1)
  proc_time_n <- proc.time() - ptm
  matrix_time[i] = proc_time_n[[3]] 
}
time_compare_table <- data.frame(data_size,hash_time,matrix_time)
#time_compare_table produces results for comparison to table 1
```

```{r, cache=TRUE}
time_compare_table
```

Wyniki czasowe są inne, ale wynika to z użycia innego sprzętu. Wnioski pozostają te same.
```{r, cache=TRUE, echo=FALSE}
library(png)
library(grid)

img <- readPNG("extra/GeospatialPointDensity/03.png")
grid.raster(img)
```

## Problemy
- trzeba dodatkowo skonfigurować dostęp do API Google'a
- API Google'a jest płatne

## Jak naprawić
- trzeba zapłacić Google'owi za dostęp do API

### Session info
```{r, echo=FALSE, cache=TRUE}
sessionInfo()
```